% Thesis Acknowledgements ------------------------------------------------
\phantomsection
\chapter*{Acknowledgements}
\markboth{\MakeUppercase{Acknowledgements}}{}
\addcontentsline{toc}{chapter}{Acknowledgements}

\if0
Doing a PhD was a long and exciting journey, which would not be possible without the help and support of many people. First of all I am most grateful to my supervisor Prof. Dr. Jianwei Zhang for giving me the opportunity to pursue a PhD at the University of Hamburg and providing me such a good and liberal academic environment. 

Next, I would like to extend my thanks to my daily supervisor and good friend Prof. Dr. Houxiang Zhang, whose support was always there for both technical and personal problems, not only in the first two years of my study when he was in Hamburg, but also for the second two years after he moved to {\AA}lesund. His constructive criticism helped focus my ideas and his constant encouragement kept me going in spite of many stumbling blocks on the road.    

Writing a dissertation is no easy task, but the same can be said of reviewing it. I would like to thank all the people who helped by reviewing parts of this work, especially my external reviewers --- Prof. Dr. Reinhard Koch and Dr. Peer Stelldinger. 

%I have to say, without your encouragement, I was almost going to drop when the traffic accident came to me while I had been ill for a long time. 

All the members of our TAMS group are greatly acknowledged, the time spent with you was wonderful. I own a great deal to Tatjana (Lu) Tetsis, thank you for helping me so much during the past time. My sincere thanks also go to Benjamin Adler for always being excited about my problems and ideas, always sharing his ideas with me, and the engaging discussions we had during and after work. 

I am grateful to my former colleagues from NuBot, Huimin Lu, Xiangke Wang, and Shaowu Yang are especially acknowledged, thanks a lot for valuable comments and suggestions on my conference and journal papers, as well as this dissertation. 

%I am thankful to all the people who helped by reviewing this work, they are Dr. Norman Hendrich, Shaowu Yang, Benjamin Adler, Weiwei Kong, and Jie Liang; especially my external reviewers --- Prof. Dr. Reinhard Koch and Dr. Peer Stelldinger.   

Being away from my family was not easy, however, many friends from Hamburg and other places provided another family away from home. I own special thanks to all of my friends. In this regard, Jianhua Zhang, Guoyuan Li, Gang Cheng, Bo Sun, and Weiwei Kong deserve special mention.

Finally, I would like to thank the people closest to me for their love and support --- my parents and brother, my girl friend Fang, especially to my little nephew who brings a lot of happy moments.  
\fi
% ------------------------------------------------------------------------

\vspace*{5mm}

\hfill Benjamin Adler

\hfill Hamburg, May 2014
